QSO decomposition

### 2018-12-12 manuscript/manuscript.tex
go again through the paper

\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{2}, John Silverman\altaffilmark{5}, Simon Birrer\altaffilmark{3}, Malte Schramm\altaffilmark{2}, Federica, Angelea
 }
 \email{dxh@astro.ucla.edu}
% Dandan Xu, Giulia, Anupreeta, Chih-Fan, Daniel, Chris, Phil Marshall, Dominique,

\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{3}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{4}{Department of Physics, University of California, Davis, CA 95616, USA}
\altaffiltext{5}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}

\begin{abstract}
To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written.  To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
%skeleton of introduction
%\\
%1. Introduce the ML relation and why understand its evolution is important.\\
%2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
%3. The 4000A by HST band.
%3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$. Recent works by H0liCOW7\\
%4. In this paper, we study the ML relation up to redshift 1.7.

Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh- stellar mass (\smass)  and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution. 
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. In theory, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver. 
However, for a different view, \textcolor{blue}{Peng 2007 and Jahnke 2011} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time. During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN. The work by \textcolor{blue}{Park, Treu, Woo, P06, H0licow7} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the recent works by \textcolor{blue}{Bennert et al. 2011, Woo 2008} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, some studies are consistent with no evolution \textcolor{blue}{Schramm+Silverman 2013, Sun et al. 2015, Cisternas et al. 2011}.

Despite the great amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works. First, the inherent uncertainties in BH mass estimates using the virial method. Especially, many studies rely on \mbh\ estimates using the \Mgii\ or \Civ\ line that may have unknown systematics when compared to local samples with masses based on broad Balmer lines (i.e. \halpha\ and \hbeta). Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties. It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \textcolor{blue}{H0licow6, Peng06, H0licow7}. Equally important,
the selection effects and their impact on the observed need to be taken well into account. For instance, it has been demonstrated \textcolor{blue}{Schulze + Wisotzki (2011, 2014))} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. Even considering this selection effect, an evolution of the scaling relations is expected from simulations \textcolor{blue}{DeGraf et al. (2015} and with respect to the bulge mass.

To make progress, on one hand, it is essential to making use of a larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh. On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation.

In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \textcolor{blue}{(Aird et al. 2015)}.  At this redshift range, we measure 32 host galaxies properties using \hst/WFC3 imaging data and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoid the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems of our sample also have \hst/ACS-F814W image. The multi-band information provide reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7 (\sim0.23$ dex).

@@

Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{red}{\bf (32+4?, the information of these four sample?)}. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf (H0licow7)}.
For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.

@@

%Drizzling, background noise...
For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 and a \texttt{gaussian} kernel. The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).
The noise level maps of the imaging data are a requirement in the study. The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. To accurately measure the photometry, we also adopt the {\sc photutils} to estimate the background light which could come from both the sky and the detector.

@@

21/32 of our sample have rest-frame UV images by \textcolor{blue}{Scoville, et al. 2007} %arxiv: 0702359}.
Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method. The kinematics of the broad-line region trace the gravitational field of the central black hole, assuming the motion of the broad-line region (BLR) gas is virialised. In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. The virial method builds on these reverberation mapping results and is directly calibrated to the \mbh.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to this paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we adopt the list of consistent recipes \textcolor{blue}{McGill et al. (2008), H0licow7} to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for this study, especially when the nuclear image is unresolved with light distributed as the point source. Moreover, the PSF in known to be vary according to their frame position and the intensity. Thus, we build a library of PSFs which we select the bright, isolated, unsaturated PSF stars across all the observed field. Thanks to the available multi-wavelength data \textcolor{blue}{(Laigle et al. 2016)}, we are able to know the positions of stars nearby the QSO field and thus select a proper position and orientation of the HST frame to cover as much PSFs stars as possible.

We claim that, by building this library, the assumption is that the overall PSFs herein indicates all the possible PSF shape for each QSO. Since two filter, i.e. F140W and F125W, are selected for different samples, we selected 78 and 36 PSFs for the samples observed by F140W and F125W, respectively.

In the next subsection, we carry out the QSO decomposition using each PSF. We rank their performance based on the goodness so that the final inference of the host properties are weighted from the top-rank PSFs.

\subsubsection{Surface Photometry modeling method}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy. Following common practice, we assume the unresolved nuclear as a scaled PSF image, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be even more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample. We fit the objects which close to the QSO as the another \sersic\ model, to minimize the impact of their light.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \textcolor{blue}{(arXiv:1803.09746)}, to decompose the host and nuclear image. The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package. 
The flexibility of this package enable us to turn off the lensing channel and carry out the decomposition.
We have tested that the inference by \lenstronomy\ could have consistent result compared to {\sc Galfit}. \textcolor{red}{Will talk more in this part.}

%Introduce the final inference using fitting:
For each QSO system, the final host properties is inferred in several steps. First, we fit the flux distribution using each PSFs in the library. Given the QSO imaging data, PSF and noise level, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals. In this step, we infer the best-fit parameters for each PSFs in the library and the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval. However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}. In the second step, we rank the performance of each PSF based on the reduced $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property. The weights for each PSF is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(-\frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2\alpha \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is the inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
\end{eqnarray}

%ECDFS-358 and CID206

In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized result of each system inferred by \lenstronomy. We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}. In Figure~\ref{fig:flux_r_n_corner}, we summarize the relation among the inferred values of: \Reff, \sersic\ $n$, and host to total flux ratio.

%The inference of F814w data.
Likewise, for the 18 systems with ACS/F184W images, we infer their host properties using the same approach. There are in total 174 star-like PSFs in the fitting library. We assumed the shape of the galaxy are consistent between the ACS and WFC3. Since the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band, we believe the inferred information of the galaxy shape by IR band are superior to the one by UV band. Thus, while fitting the host flux at ACS band, we fix the \Reff\ and \sersic\ $n$ to the value by IR.

@@

%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.

\subsubsection{Host luminosity}
\textcolor{red}{To be written:}
1.K-correction to infer the rest frame R-band.\\
* The galaxy template inferred by the joint fitting of the SED and the host flux ratio by us.

@@

\subsection{BH masses}
\label{mbh}
Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.

To avoid any systematic bias between our samples and the literature samples, we cross-calibrate the \mbh\ by adopting the self-consistent recipes as used by \textcolor{blue}{H0licow7, McGill et al. (2008)}. Overall, we adopt the following virial formalism for the \halpha\ and \hbeta\ emission line:

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}

>>>>

\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{1}, John Silverman\altaffilmark{3}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Simon Birrer\altaffilmark{1}, Malte Schramm\altaffilmark{6}, Andreas Schulze\altaffilmark{6}
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, Università Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}
To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written.  To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
%\citep[e.g.,][]{Park15,Kormendy13}

Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN. The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

Despite the great amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works. First, the inherent uncertainties in BH mass estimates using the virial method. Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties. It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Equally important,
the selection effects and their impact on the observed need to be taken well into account. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.

To make progress, it is essential to make use of the larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh. On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.

In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{blue}{\bf (32+4?, the information of these four sample?)}. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.

To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.

@@

%Drizzling, background noise...
For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 with a \texttt{gaussian} kernel. \textcolor{blue}{The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).}
To accurately estimate the background light which could come from both the sky and the detector, we also adopt the {\sc photutils} to measure the photometry.

@@

21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. %arxiv: 0702359}.
Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the motion of the BLR gas is virialised by the gravity. In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to this paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt the list of consistent ones to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the QSO imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations. The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}. Empirical PSF stars are considered better than the simulated ones, since they we observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by cutting out the isolated, unsaturated PSF stars with high S/N from the overall QSO field. We first collect the identified stars as candidates which are listed in the COSMOS2015 catalog by \citet{Laigle2016}. However, since a lot of bright stars with intensity similar to the QSOs are excluded by \citet{Laigle2016}, we visually select these star-like PSF as candidates. Finally, we remove the non-ideal PSF candidates by inspecting their intensity, FWHM, central symmetry and any that were contaminated by background objects. To summarize, we selected 78 and 36 PSFs from the field observed by filter F140W and F125W, respectively.

We stress that, by building this library, we assume that the PSFs herein bracket all the possible PSF light distribution which fits our imaging data. Therefore, the inference from each PSF will include the true answer. In the next subsection, we carry out the QSO decomposition using each PSF. We rank their performance based on the goodness (i.e. $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy. Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be even more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample. Furthermore, we fit the galaxies which close to the QSO as the \sersic\ model, to account for the contamination of their light.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy}, to decompose the host and nuclear light. The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package. 
The flexibility of this package enable us to turn off the lensing channel and carry out this task\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modelling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}. The input ingredients to \lenstronomy\ includes:
\begin{enumerate}
\item \hst\ AGN imaging data. -- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ cover sufficient QSO light our samples. By default, we cut out the AGN image to a $61\times61$ pixels box (i.e. $4''\times 4''$). 
\item Noise level map -- The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. 
\item PSF -- The PSF are directly taken from the PSF library. Usually, mismatch exists when subtract the AGN as the scaled PSF, especially at the central parts. We assume that the overall inference based on each PSF bracket the best one as one can obtain, given the flexibility of the library. We also note that, in the lens modelling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.  However, this approach collects the information of the lensing feature which is not suitable to our case. If one forces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
\end{enumerate}

%Introduce the final inference using fitting:
Focusing on each QSO system, its host light information is inferred through several steps. First, we fit the flux distribution using each PSFs in the library. Given the fitting ingredients, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals. In this step, we apply the Particle Swarm Optimizer (PSO) to optimize the best-fit parameters based on the imaging likelihood. Running through the library, we record the inference based on each PSF together with the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval. However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}. In the second step, we rank the performance of each PSF based on the $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property. The weights for each PSF is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is the inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
\end{eqnarray} 
Note that since each QSO system has different seeing condition, the top-8 PSFs are different for each system.

%ECDFS-358 and CID206
In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized results inferred by \lenstronomy. In each, we show the images, best-fit models, image subtract point source (i.e. host) and the residuals for every systems. As an example, we also show the weighting process for system CID1174 in Table~\ref{tab:weight_CID1174}. To quickly overview our inference, we summarize them as relations between: 1) effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

%The inference of F814w data.
18/32 systems in COSMOS field have ACS/F184W imaging data. Likewise, we infer their host properties using the same approach. The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library. While fitting the host light, we fix the \Reff\ and \sersic\ $n$ as the value inferred by WFC3/IR, assuming that the shape of the galaxy are consistent between ACS and WFC3. We believe the inferred information of the galaxy shape by IR imaging are superior to the one by UV band, considering the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band.

@@

\subsubsection{Host luminosity}
%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
\textcolor{red}{To be written:}
1.K-correction to infer the rest frame R-band.\\
* The galaxy template inferred by the joint fitting of the SED and the host flux ratio by us.

@@

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as used by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator are very close between the two reference. Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent. Therefore, we directly adopt virial formalism from \citet{Schulze2018}:
\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
